---
title: "Bachelor Project"
author: "Sofie Ditmer"
date: "9/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages
```{r}
library(pacman)
pacman::p_load(readtext,tidyverse, pastecs, WRS2, tidyselect, brms, rethinking, bayesplot, udpipe, stopwords, textclean)
#devtools::install_github("quanteda/stopwords")
```

# Load data
First we load one subset to test the operations on to make sure that everything works adequately
```{r}
subset1 <- read.delim("Formatted_Data/subset1.txt", header = FALSE, quote="", fill=FALSE)
```

Now we load the rest of the subsets. Since the datafile is too large (6 GB), we had to split it into multiple files to it all into R.
```{r}
subset1 <- read.delim("Formatted_Data/subset1.txt", header = FALSE, quote="", fill=FALSE)
subset2 <- read.delim("Formatted_Data/subset2.txt", header = FALSE, quote="", fill=FALSE)
subset3 <- read.delim("Formatted_Data/subset3.txt", header = FALSE, quote="", fill=FALSE)
subset4 <- read.delim("Formatted_Data/subset4.txt", header = FALSE, quote="", fill=FALSE)
subset5 <- read.delim("Formatted_Data/subset5.txt", header = FALSE, quote="", fill=FALSE)
subset6 <- read.delim("Formatted_Data/subset6.txt", header = FALSE, quote="", fill=FALSE)
subset7 <- read.delim("Formatted_Data/subset7.txt", header = FALSE, quote="", fill=FALSE)
subset8 <- read.delim("Formatted_Data/subset8.txt", header = FALSE, quote="", fill=FALSE)
subset9 <- read.delim("Formatted_Data/subset9.txt", header = FALSE, quote="", fill=FALSE)
subset10 <- read.delim("Formatted_Data/subset10.txt", header = FALSE, quote="", fill=FALSE)
subset11 <- read.delim("Formatted_Data/subset11.txt", header = FALSE, quote="", fill=FALSE)
subset12 <- read.delim("Formatted_Data/subset12.txt", header = FALSE, quote="", fill=FALSE)
subset13 <- read.delim("Formatted_Data/subset13.txt", header = FALSE, quote="", fill=FALSE)
subset14 <- read.delim("Formatted_Data/subset14.txt", header = FALSE, quote="", fill=FALSE)
subset15 <- read.delim("Formatted_Data/subset15.txt", header = FALSE, quote="", fill=FALSE)
subset16 <- read.delim("Formatted_Data/subset16.txt", header = FALSE, quote="", fill=FALSE)
subset17 <- read.delim("Formatted_Data/subset17.txt", header = FALSE, quote="", fill=FALSE)
subset18 <- read.delim("Formatted_Data/subset18.txt", header = FALSE, quote="", fill=FALSE)
subset19 <- read.delim("Formatted_Data/subset19.txt", header = FALSE, quote="", fill=FALSE)
subset20 <- read.delim("Formatted_Data/subset20.txt", header = FALSE, quote="", fill=FALSE)
subset21 <- read.delim("Formatted_Data/subset21.txt", header = FALSE, quote="", fill=FALSE)
subset22 <- read.delim("Formatted_Data/subset22.txt", header = FALSE, quote="", fill=FALSE)
subset23 <- read.delim("Formatted_Data/subset23.txt", header = FALSE, quote="", fill=FALSE)
subset24 <- read.delim("Formatted_Data/subset24.txt", header = FALSE, quote="", fill=FALSE)
subset25 <- read.delim("Formatted_Data/subset25.txt", header = FALSE, quote="", fill=FALSE)
subset26 <- read.delim("Formatted_Data/subset26.txt", header = FALSE, quote="", fill=FALSE)
subset27 <- read.delim("Formatted_Data/subset27.txt", header = FALSE, quote="", fill=FALSE)
subset28 <- read.delim("Formatted_Data/subset28.txt", header = FALSE, quote="", fill=FALSE)
subset29 <- read.delim("Formatted_Data/subset29.txt", header = FALSE, quote="", fill=FALSE)
subset30 <- read.delim("Formatted_Data/subset30.txt", header = FALSE, quote="", fill=FALSE)
subset31 <- read.delim("Formatted_Data/subset31.txt", header = FALSE, quote="", fill=FALSE)
subset32 <- read.delim("Formatted_Data/subset32.txt", header = FALSE, quote="", fill=FALSE)
subset33 <- read.delim("Formatted_Data/subset33.txt", header = FALSE, quote="", fill=FALSE)
subset34 <- read.delim("Formatted_Data/subset34.txt", header = FALSE, quote="", fill=FALSE)
subset35 <- read.delim("Formatted_Data/subset35.txt", header = FALSE, quote="", fill=FALSE)
subset36 <- read.delim("Formatted_Data/subset36.txt", header = FALSE, quote="", fill=FALSE)
subset37 <- read.delim("Formatted_Data/subset37.txt", header = FALSE, quote="", fill=FALSE)
subset38 <- read.delim("Formatted_Data/subset38.txt", header = FALSE, quote="", fill=FALSE)
subset39 <- read.delim("Formatted_Data/subset39.txt", header = FALSE, quote="", fill=FALSE)
subset40 <- read.delim("Formatted_Data/subset40.txt", header = FALSE, quote="", fill=FALSE)
subset41 <- read.delim("Formatted_Data/subset41.txt", header = FALSE, quote="", fill=FALSE)
subset42 <- read.delim("Formatted_Data/subset42.txt", header = FALSE, quote="", fill=FALSE)
subset43 <- read.delim("Formatted_Data/subset43.txt", header = FALSE, quote="", fill=FALSE)
subset44 <- read.delim("Formatted_Data/subset44.txt", header = FALSE, quote="", fill=FALSE)
subset45 <- read.delim("Formatted_Data/subset45.txt", header = FALSE, quote="", fill=FALSE)
subset46 <- read.delim("Formatted_Data/subset46.txt", header = FALSE, quote="", fill=FALSE)
subset47 <- read.delim("Formatted_Data/subset47.txt", header = FALSE, quote="", fill=FALSE)
subset48 <- read.delim("Formatted_Data/subset48.txt", header = FALSE, quote="", fill=FALSE)
subset49 <- read.delim("Formatted_Data/subset49.txt", header = FALSE, quote="", fill=FALSE)
subset50 <- read.delim("Formatted_Data/subset50.txt", header = FALSE, quote="", fill=FALSE)
subset51 <- read.delim("Formatted_Data/subset51.txt", header = FALSE, quote="", fill=FALSE)
subset52 <- read.delim("Formatted_Data/subset52.txt", header = FALSE, quote="", fill=FALSE)
subset53 <- read.delim("Formatted_Data/subset53.txt", header = FALSE, quote="", fill=FALSE)
subset54 <- read.delim("Formatted_Data/subset54.txt", header = FALSE, quote="", fill=FALSE)
subset55 <- read.delim("Formatted_Data/subset55.txt", header = FALSE, quote="", fill=FALSE)
subset56 <- read.delim("Formatted_Data/subset56.txt", header = FALSE, quote="", fill=FALSE)
```

# TESTING OPERATIONS ON SUBSET1 #
# Load UDpipemodel
```{r}
# Get danish model
danish <- udpipe_download_model(language = "danish")
str(danish)

# Load danish model
udmodel_danish  <- udpipe_load_model(file = "danish-ddt-ud-2.4-190531.udpipe")

```

Make text into lowercase, remove punctuation, and remove numbers
```{r}
subset1[,1] <- tolower(subset1[,1]) # make it lower case
subset1[,1] <-  gsub("[[:punct:]]", "", subset1[,1]) # remove punctuation
subset1[,1] <- gsub("[[:digit:]]", "", subset1[,1]) # remove numbers
```

Removing stopwords
```{r}
# Using the stopwords package
list_of_stopwords <- stopwords::stopwords("da", source = "snowball")

# Remove stopwords from subset data
stopwords_regex = paste(stopwords('da'), collapse = '\\b|\\b')
stopwords_regex = paste0('\\b', stopwords_regex, '\\b')
subset1[,1] <- stringr::str_replace_all(subset1[,1], stopwords_regex, '')

```

NLP: tokenization, tagging, lemmatization, dependency parsing
```{r}
x <- udpipe_annotate(udmodel_danish, x = subset1[,1])
x <- as.data.frame(x)
str(x)
table(x$upos)
```

Creating the right format that can be used in Python
```{r}
x2 <- x

# Remove "doc" so we only have numbers
x2$doc_id <- stringr::str_replace_all(x2$doc_id, "doc", "")
x2$doc_id <- as.numeric(x2$doc_id)

# Collapse
x2 <- x2 %>%
  select(doc_id, lemma) %>% 
  group_by(doc_id) %>% 
  summarize(sentence = str_c(lemma, collapse = ", ")) %>% 
  arrange()

# Remove doc_id column
x2$doc_id <- NULL

# Remove commas
x2$sentence <- gsub("[[:punct:]]", "", x2$sentence)

# Quotations around words
#x2$sentence <- sapply(strsplit(x2$sentence, '[,]'), function(x) toString(sQuote(x)))
#x2$sentence <- stringr::str_replace_all(x2$sentence, " ", "")
# Insert space after comma
#x2$sentence <- textclean::add_comma_space(x2$sentence)
#x3$sentence <- gsub("[[:punct:]]", "", x3$sentence) # replacing punctation with nothing
```

Making a csv-file
```{r}
write.csv(x2, file = "preprocessed_subset1.csv", row.names = FALSE, col.names = NA)
```

# RUNNING OPERATIONS ON ALL SUBSETS ##
Now that we have tried out the operations on a single subset, we will do it on all subsets
```{r}
# Make a list of subsets
list_of_subset_dataframes <- list(subset2,subset3, subset4, subset5, subset6, subset7, subset8, subset9, subset10, subset11, subset12, subset13, subset14, subset15, subset16, subset17, subset18, subset19, subset20, subset21, subset22, subset23, subset24, subset25, subset26, subset27, subset28, subset29, subset30, subset31, subset32, subset33, subset34, subset35, subset36, subset37, subset38, subset39, subset40, subset41, subset42, subset43, subset44, subset45, subset46, subset47, subset48, subset49, subset50, subset51, subset52, subset53, subset54, subset55, subset56)

# Apply all preprocessing functions on all subsets
list_of_preprocessed_subsets <- lapply(df.list, function(x) rowMeans(subset(x, select = c(start, stop)), na.rm = TRUE))

# Add subset1 to the preprocessed list
list_of_subset_dataframes <- list(subset1, subset2,subset3, subset4, subset5, subset6, subset7, subset8, subset9, subset10, subset11, subset12, subset13, subset14, subset15, subset16, subset17, subset18, subset19, subset20, subset21, subset22, subset23, subset24, subset25, subset26, subset27, subset28, subset29, subset30, subset31, subset32, subset33, subset34, subset35, subset36, subset37, subset38, subset39, subset40, subset41, subset42, subset43, subset44, subset45, subset46, subset47, subset48, subset49, subset50, subset51, subset52, subset53, subset54, subset55, subset56)
```















